Voting without ID

### 2024-02-13 paper/paper.qmd
Updated table 1 caption that corresponds to map

---
title: "Voting"
author: "Emily Su"
thanks: "Data and code are available at: https://github.com/moonsdust/toronto-collisions. The replication on Social Science Reproduction Platform can be found here: https://www.socialsciencereproduction.org/reproductions/c0db16d9-e70e-4bbc-85d2-f7137a0e8c47/index"
date: today
date-format: "YYYY MMMM D"
abstract: "Abstract."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

## Tables from Results {#sec-tablesfromresults}
```{r}
#| label: tbl-votermap
#| tbl-cap: Number of United States election voters across Texas counties in 2016 without IDs
#| echo: false
#| warning: false
#| message: false

>>>>

---
title: "Voting without ID"
author: "Emily Su"
thanks: "Data and code are available at: https://github.com/moonsdust/toronto-collisions. The replication on Social Science Reproduction Platform can be found here: https://www.socialsciencereproduction.org/reproductions/c0db16d9-e70e-4bbc-85d2-f7137a0e8c47/index"
date: today
date-format: "YYYY MMMM D"
abstract: "Abstract."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

## Tables from Results {#sec-tablesfromresults}
```{r}
#| label: tbl-votermap
#| tbl-cap: Number of voters across Texas counties during 2016 United States election without proper ID
#| echo: false
#| warning: false
#| message: false
